% ====================
% EXPERIENCE A
% ====================
\subsection{{Frontend Developer Intern\hfill Sept 2023 --- Present }}
\subtext{\href{https://targettechnology.in/}{Target Technology} \hfill Kolkata, West Bengal}
\begin{zitemize}
    \item I leveraged \textbf{React}, \textbf{Tailwind CSS}, and \textbf{JavaScript} skills to craft visually appealing and responsive web interfaces. 
    \item Collaborated closely with teams, translating designs into seamless user experiences. Optimized website performance for diverse platforms, enhancing project efficiency.
\end{zitemize}


% ====================
% EXPERIENCE B
% ====================
\subsection{{Full Stack Developer Intern\hfill July 2023 --- August 2023}}
\subtext{\href{https://infotrixs.com/}{INFOTRIXS} \hfill  Maharashtra}
\begin{zitemize}
    \item Built a fitness tracker with a dynamic team using \textbf{React} and \textbf{Tailwind CSS}. Collaborated closely, honed problem-solving skills, and thrived in an agile environment. 
    \item Gained hands-on experience in full-stack development, fostering a passion for innovative solutions. Grateful to INFOTRIXS for the invaluable mentorship. Excited to apply my skills to future projects.
\end{zitemize}
% ====================
% Letter of Recommendation
% ====================
\begin{zitemize}
\subsection{{Letter of Recommendation}}
\item You can access my Letter of Recommendation through the following link: \href{https://drive.google.com/file/d/1CgP45vZIpdOrJJdlWFLo5sY55WQj5FiL/view?usp=drivesdk}{Google Drive Link}.
\end{zitemize}
% ====================
% Completion Certificate
% ====================
\begin{zitemize}
\subsection{{Completion Certificate}}
\item My completion certificate can be found at: \href{https://drive.google.com/file/d/1DF9omNonCkAQRWrWYLqhWcF5RD2DxaC6/view?usp=drivesdk}{Google Drive Link}.
\end{zitemize}

% ====================
% EXPERIENCE C
% ====================
\subsection{{Web Developer Intern\hfill Aug 2022 --- Aug 2022 }}
\subtext{\href{https://bharatintern.live/b/i/index.html}{Bharat Intern} \hfill Madhya Pradesh}
\begin{zitemize}
    \item As a Web Developer Intern at Bharat Intern, I had the opportunity to work on exciting projects, including the development of a Netflix clone using \textbf{Tailwind CSS} and \textbf{JavaScript}. I collaborated with a talented team to bring this project to life, applying my skills in web development to create an engaging and user-friendly platform. 
    \item This internship not only enhanced my technical abilities but also provided valuable insights into teamwork and project management. I'm grateful for the experience and look forward to applying my expertise to future endeavors.
\end{zitemize}
% ====================
% Completion Certificate
% ====================
\begin{zitemize}
\subsection{{Completion Certificate}}
\item My completion certificate can be found at: \href{https://drive.google.com/file/d/1kW9k5gszJlIEXFur_P-q36PIus9H_Qyk/view?usp=drivesdk}{Google Drive Link}.
\end{zitemize}


